Cluster Difference Imaging Photometric Survey. I. Light Curves of Stars in Open Clusters from TESS Sectors 6 \& 7

### 2019-09-20 paper_I/ms.tex
add comments per referee report

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt,twocolumn,tighten]{aastex62}
%\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{comment}

@@

\newcommand{\stscilink}{\url{archive.stsci.edu/prepds/cdips}}
\newcommand{\stscivetlink}{\url{archive.stsci.edu/prepds/cdips/vetting}}

@@

%\NewPageAfterKeywords

@@

After subtracting the background, we mask out saturated pixels using a
fixed saturation level of $8\times10^4$ analog-to-digital units (ADU).
This value was chosen based on the onset of bleeding charge trails in
the images, and is slightly greater than the saturation level of
$2\times10^5$ electrons, or about $4\times10^4\,{\rm ADU}$, reported
by \citet{vanderspek_2018}.  As a consequence, we do not analyze stars
brighter than $T\approx 6.5$.  As described by \citet{Pal_2009}, the
pixel masks are metadata attached to the image file, and are only
applied to the pixel values during the specific image processing steps
in which they are necessary ({\it e.g.}, convolution). We also extend
the masks beyond purely saturated pixels to ``bloomed'' pixels
horizontally and vertically adjacent to the saturated pixels (see
Figure~6 of \citealt{Pal_2009}).

@@

A separate step for each light curve can then be to fit out linear
correlations of stellar magnitude with ``external parameters'' (EPD,
\citealt[][]{bakos_2010,huang_high-precision_2015}).  For ground-based
data these parameters might include zenith angle, or changing PSF
shape.  For TESS data, they might include CCD temperature, or the
angles of the Moon and Earth relative to each camera's boresight.
They might also include the standard deviation of the spacecraft
quartnerion time-series \citep{vanderburg_hr858_2019}.  Some example
``external'' parameters that we include with our light curves are
shown as functions of time in
Figure~\ref{fig:external_parameter_timeseries}.

@@

\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\documentclass[12pt,twocolumn,tighten]{aastex62}
\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
%\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{comment}

@@

\newcommand{\stscilink}{\textsc{\url{archive.stsci.edu/hlsp/cdips}}}
\newcommand{\stscivetlink}{\url{archive.stsci.edu/prepds/cdips/vetting}}

@@

%\NewPageAfterKeywords
\listofchanges

@@

After subtracting the background, we mask out saturated pixels using a
fixed saturation level of $8\times10^4$ analog-to-digital units (ADU).
This value was chosen based on the onset of bleeding charge trails in
the images, and is \deleted{slightly}\added{a factor of two} greater than the 
saturation level of
$2\times10^5$ electrons, or about $4\times10^4\,{\rm ADU}$, reported
by \citet{vanderspek_2018}.  As a consequence, we do not analyze stars
brighter than $T\approx 6.5$\deleted{.}\added{, even though the TESS CCID-80 
CCDs conserve charge across bloom trails up to at least
$T\approx 4$ \citet{vanderspek_2018}.}
As described by \citet{Pal_2009}, the
pixel masks are metadata attached to the image file, and are only
applied to the pixel values during the specific image processing steps
in which they are necessary ({\it e.g.}, convolution). We also extend
the masks beyond purely saturated pixels to ``bloomed'' pixels
horizontally and vertically adjacent to the saturated pixels (see
Figure~6 of \citealt{Pal_2009}).

@@

A separate step for each light curve can then be to fit out linear
correlations of stellar magnitude with ``external parameters'' (EPD,
\citealt[][]{bakos_2010,huang_high-precision_2015}).  For ground-based
data these parameters might include zenith angle, or changing PSF
shape.  For TESS data, they might include CCD temperature, or the
angles of the Moon and Earth relative to each camera's boresight.
They might also include the standard deviation of the spacecraft
\deleted{quartnerion}\added{quaternion} time-series
\citep{vanderburg_hr858_2019}.  Some example ``external'' parameters
that we include with our light curves are shown as functions of time
in Figure~\ref{fig:external_parameter_timeseries}.

@@

\listofchanges
\end{document}
